---
title: CCHA site assessments
author: "MW Beck"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, echo = T, message = F, warning = F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

box::use(
  here[...], 
  ggplot2[...], 
  tidyr[...],
  dplyr[...], 
  ggridges[...],
  reactable[...],
  lubridate[ymd, year], 
  stringr[str_wrap],
  forcats[fct_reorder2], 
  htmltools[h5], 
  htmlwidgets[prependContent]
)

source(here('R/funcs.R'))

load(file = here('data/vegdat.RData'))
load(file = here('data/treedat.RData'))

thm <- theme_minimal(base_size = 14) + 
  theme(
    panel.grid.minor = element_blank() 
  )

# test args
site <- 'Cockroach'
sp <- 'Avicennia germinans'
```

Plot showing number of times a zone was identified across transects, dates.

```{r, fig.height = 5, fig.width = 7}
zonecnt_plo(vegdat, thm)
```

An evaluation of a single species across all sites, can be shown as frequency occurrence across the transect or mean percent basal cover. This example shows frequency occurrence of *Avicennia germinans*. 

```{r, fig.height = 4, fig.width = 12}
sppsum_plo(vegdat, sp, var = 'fo', qrt = NULL, thm = thm)
```

And now average percent basal cover. 

```{r, fig.height = 4, fig.width = 12}
sppsum_plo(vegdat, sp, var = 'cover', thm = thm)
```

A table of species frequency occurrence by zone, over time: 

```{r}
sitezonesum_tab(vegdat, site = site)
```

Same thing but as percent basal cover.

```{r}
sitezonesum_tab(vegdat, site = site, var = 'cover')
```

A plot of sum of percent basal cover for top species and across zones.

```{r, fig.height = 6, fig.width = 10}
sitesum_plo(vegdat, site, vegsel = 8, var = 'cover', thm = thm)
```

A plot of sum of percent basal cover for top species and select zones.

```{r, fig.height = 6, fig.width = 10}
sitesum_plo(vegdat, site, vegsel = 8, var = 'cover', zone = c('Mangrove', 'Freshwater Marsh'), thm = thm)
```

Tabular summary of tree data by site, species.

```{r}
treesum_tab(treedat, site = site, byspecies = T, var = 'trees_ha')
```

Same table as above, but aggregated across species.

```{r}
treesum_tab(treedat, site = site, byspecies = F, var = 'trees_ha')
```

Tree summary plot by site, species.

```{r, fig.height = 6, fig.width = 10}
treesum_plo(treedat, site = site, byspecies = T, var = 'trees_ha', thm = thm)
```

Tree summary plot, but aggregated across species.

```{r, fig.height = 6, fig.width = 10}
treesum_plo(treedat, site = site, byspecies = F, var = 'trees_ha', thm = thm)
```
